---
author: "Max Blasdel"
title: "Python Functions"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---
<style>
.Python:hover{
  background-color:#dedfe0;
}
</style>

# Using Reticulate

Simple example of a report that could be made with R markdown, calling Python functions then adding some silliness with JavaScript.

Load the necessary R libraries and tell the document which python interpreter it should be using. Notice the commented out `py_install` calls which only need to be run once.

```{r setup, include=T}
library(reticulate)
library(tictoc)

use_python("../python/bin/python3")

# py_install("paramiko", pip = T)
# py_install("pandas")
# py_install("Pillow", pip = T)
```

Source the python functions as if they were R files. These function don't return anything, just run a couple of python scripts to download files and clean data.

I time the operation so that I can output this value in the report.
<img id="py" src="https://upload.wikimedia.org/wikipedia/commons/c/c3/Python-logo-notext.svg" style="display:none;">
```{r, class.source="Python"}
tic()
source_python("download_pictures.py")
source_python("clean_metadata.py")
toc(log = T)
```

The above operation ran in `r tic.log()`

Below shows some of the versatility of R markdown and the ability to run different languages through R as shown above or independently with separate code chunks.

```{js}
var elements = document.getElementsByClassName("Python");

for (var i = 0; i < elements.length; i++) {
    elements[i].addEventListener('click', function() {
    document.getElementById("py").style.display="block"
    }, false);
}
```

